Are we living in a depressive society?

### 2024-04-02 outputs/paper/paper.qmd
commit

@@

## First discussion point {#sec-first-point}

@@

## Second discussion point

## Third discussion point

## Weaknesses and next steps

@@

@@

>>>>

## Methodology

## Features

## Trend in US Anxiety and Depressive Disorder Rates

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-andtrend-graph
#| fig-cap: "Trend in US Anxiety and Depressive Disorder Rates"

install.packages("here")

# Load necessary libraries
library(tidyverse)
library(lubridate)
library(here)

# Load the dataset
data <- read.csv(file = here::here("inputs/data/Anxiety_or_Depression.csv"))

# Filter the dataset for 'National Estimate' under 'Group' column and select indicators of interest

filtered_data <- data %>%
  filter(Group == "National Estimate" & Indicator %in% c("Symptoms of Anxiety Disorder", 
                                                         "Symptoms of Depressive Disorder", 
                                                         "Symptoms of Anxiety Disorder or Depressive Disorder"))

# Create a YearMonth column from 'Time Period Label'

filtered_data <- filtered_data %>%
  mutate(YearMonth = as.Date(paste0(sub("^(\\d{4}).+", "\\1", `Time Period Label`), 
                                    ".", 
                                    sub(".+(\\d{2})$", "\\1", `Time Period Label`), 
                                    "01"), format="%Y.%m.%d"))

# Aggregate the data by YearMonth and Indicator
aggregated_data <- filtered_data %>%
  group_by(YearMonth, Indicator) %>%
  summarise(AverageValue = mean(Value, na.rm = TRUE))

# Plot the data
ggplot(aggregated_data, aes(x = YearMonth, y = AverageValue, color = Indicator)) +
  geom_line() +
  scale_x_date(date_breaks = "6 months", date_labels = "%Y.%m") +
  labs(
    title = "National Estimates of Mental Health Symptoms",
    subtitle = "Trends of Symptoms of Anxiety and Depressive Disorders",
    x = "Year",
    y = "Rate (%)",
    color = "Indicator"
  ) +
  theme_minimal()

```

## Trends in Anxiety and Depressive Disorder Rates by Population Subgroup

@@

## Findings

@@

## Ethical Implication

## Limitation

@@

## Future Research

@@

---
nocite: '@*'
---
